A systematic search for transiting planets using \KT

### 2015-02-02 ms.tex
a few words about model selection

\newcommand{\T}{\ensuremath{\mathrm{T}}}
\newcommand{\dd}{\ensuremath{\,\mathrm{d}}}
\newcommand{\bvec}[1]{{\ensuremath{\boldsymbol{#1}}}}
\newcommand{\appropto}{\mathrel{\vcenter{
  \offinterlineskip\halign{\hfil$##$\cr
    \propto\cr\noalign{\kern2pt}\sim\cr\noalign{\kern-2pt}}}}}
\newcommand{\densityunit}{{\ensuremath{\mathrm{nat}^{-2}}}}

@@

In the period search step, we use the lookup table generated by the linear
search to compute the likelihood from \eq{indtran} on a three dimensional
grid in period \period, reference time \phase, and duration \duration.
At each point, we compute the likelihood of a model where the transit depth
varies between transits and the ``correct'' simpler model where the transit
depth is constant.
The variable depth likelihood is simply the product of amplitudes from the
initial search
\begin{eqnarray}
p_\mathrm{var}(\{\flux\}_n\,|\,\period,\,\phase,\,\duration) &=&
\prod_{m=1}^{M(\period,\,\phase)} L_m \quad,
\end{eqnarray}
and the constant depth model is
\begin{eqnarray}
p_\mathrm{const}(\{\flux\}_n\,|\,\period,\,\phase,\,\duration) &=&
\prod_{m=1}^{M(\period,\,\phase)}
    \frac{L_m}{\sqrt{2\,\pi\,{\delta\bar{\depth}_m}^2}}\,\exp \left(
        -\frac{[\depth - \bar{\depth}_m]^2}{2\,{\delta\bar{\depth}_m}^2}
    \right)
\end{eqnarray}
where the maximum likelihood depth is
\begin{eqnarray}
\depth &=& {\sigma_\depth}^2\,\sum_{m=1}^{M(\period,\,\phase)}
    \frac{\bar{\depth}_m}{{\delta\bar{\depth}_m}^2}
\end{eqnarray}
and
\begin{eqnarray}
\frac{1}{{\sigma_\depth}^2} &=& \sum_{m=1}^{M(\period,\,\phase)}
    \frac{1}{{\delta\bar{\depth}_m}^2} \quad.
\end{eqnarray}

@@

>>>>

\newcommand{\BIC}{{\ensuremath{\mathrm{BIC}}}}
\newcommand{\TIC}{{\ensuremath{\mathrm{TIC}}}}
\newcommand{\T}{\ensuremath{\mathrm{T}}}
\newcommand{\dd}{\ensuremath{\,\mathrm{d}}}
\newcommand{\bvec}[1]{{\ensuremath{\boldsymbol{#1}}}}
\newcommand{\appropto}{\mathrel{\vcenter{
  \offinterlineskip\halign{\hfil$##$\cr
    \propto\cr\noalign{\kern2pt}\sim\cr\noalign{\kern-2pt}}}}}
\newcommand{\densityunit}{{\ensuremath{\mathrm{nat}^{-2}}}}

@@

In the period search step, we use the lookup table generated by the linear
search to compute the likelihood from \eq{indtran} on a three dimensional
grid in period \period, reference time \phase, and duration \duration.
At each point, we compute the likelihood of a model where the transit depth
varies between transits and the ``correct'' simpler model where the transit
depth is constant.
The variable depth likelihood is simply the product of amplitudes from the
initial search
\begin{eqnarray}
p_\mathrm{var}(\{\flux\}_n\,|\,\period,\,\phase,\,\duration) &=&
\prod_{m=1}^{M(\period,\,\phase)} L_m \quad,
\end{eqnarray}
and the constant depth model is
\begin{eqnarray}
p_\mathrm{const}(\{\flux\}_n\,|\,\period,\,\phase,\,\duration) &=&
\prod_{m=1}^{M(\period,\,\phase)}
    \frac{L_m}{\sqrt{2\,\pi\,{\delta\bar{\depth}_m}^2}}\,\exp \left(
        -\frac{[\depth - \bar{\depth}_m]^2}{2\,{\delta\bar{\depth}_m}^2}
    \right)
\end{eqnarray}
where the maximum likelihood depth is
\begin{eqnarray}
\depth &=& {\sigma_\depth}^2\,\sum_{m=1}^{M(\period,\,\phase)}
    \frac{\bar{\depth}_m}{{\delta\bar{\depth}_m}^2}
\end{eqnarray}
and the uncertainty on this depth is given by
\begin{eqnarray}
\frac{1}{{\sigma_\depth}^2} &=& \sum_{m=1}^{M(\period,\,\phase)}
    \frac{1}{{\delta\bar{\depth}_m}^2} \quad.
\end{eqnarray}

In general, the variable depth model will \emph{always} get a higher
likelihood because it is more flexible.
Therefore, to compare these two models, we use the Bayesian Information
Criterion (BIC).
The traditional definition of the BIC is
\begin{eqnarray}
-\frac{1}{2}\,\BIC_\cdot &=&
    \ln p_\cdot(\{\flux\}_n\,|\,\period,\,\phase,\,\duration)
    - \frac{J}{2} \ln N
\end{eqnarray}
where the likelihood function is maximized, $J$ is an estimate of the model
complexity and $N$ is the effective sample size.
To emphasize that $J$ and $N$ are tuning parameters of the method, we
redefine the BIC as the TIC
\begin{eqnarray}
\TIC_\cdot &=&
    \ln p_\cdot(\{\flux\}_n\,|\,\period,\,\phase,\,\duration) - \alpha
\end{eqnarray}
and we choose $\alpha$ heuristically.
For the K2 Campaign 1 dataset, we find that $\alpha \sim 1250$ leads to robust
recovery of injected signals while still being fairly insensitive to false
signals.

To limit memory consumption, in the periodic search, we actually profile (or
maximize) over \phase\ subject to the constraint that $\TIC_\mathrm{const} >
\TIC_\mathrm{var}$.

@@

To generate an initial candidate list, we start by .
